The error in Bayesian phylogenetic reconstruction when speciation co-occurs

### 2018-11-27 article.tex
Expect timing to have no effect, progress https://github.com/richelbilderbeek/razzo/issues/143

\item Summarized, we expect the error made be correlated to the number 
of species created by the multiple-birth process over the total number 
of species created:

@@

>>>>

\item To put into an explicit equation, 
we expect the error made be correlated to the number 
of species created by the multiple-birth process over the total number 
of species created:

@@

\item Due to the proportionality of the term within $f$, 
we expect the timing of a multiple births event (be it close to the
crown age or close to the present) to have no effect. Compared to a late
multiple birth event, an early multiple birth event may have a 
longer-lasting effect (as the next speciation event will be later), but it
will create less new species, as there are still fewer taxa.
